\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/training.pdf}
    \vspace{-1cm}
    \caption{Toy example. Training curves for ${\cal L}_f(\theta_f)$, ${\cal L}_r(\theta_f, \theta_r)$
             and ${\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r)$.
             Adversarial training was performed for $100$ iterations, mini-batches of size $M=128$, $K=100$ and $\lambda=50$.}
    \label{fig:toy-training}
\end{figure}

@@

\glnote{Discuss practical considerations regarding the stability of training.}
\glnote{Warn against
setting $\lambda$ too high, since it could simply force $f$ to produce unlikely
and very bad decisions.}

>>>>

\begin{figure}
    \includegraphics[width=0.48\textwidth]{figures/training.pdf}
    \vspace{-1cm}
    \caption{Toy example. Training curves for ${\cal L}_f(\theta_f)$, ${\cal L}_r(\theta_f, \theta_r)$
             and ${\cal L}_f(\theta_f) - \lambda {\cal L}_r(\theta_f, \theta_r)$.
             Adversarial training was performed for $200$ iterations, mini-batches of size $M=128$, $K=100$ and $\lambda=50$.}
    \label{fig:toy-training}
\end{figure}

@@
